\documentclass{article}
\usepackage{xcolor}
\usepackage{graphicx}

%opening
\title{Final Report}
\author{team\_we\_got\_this}

\begin{document}

\maketitle


\section*{Introduction}
	\textcolor{blue}{Describe the context for the work and the problem you are addressing. 
	Briefly summarise what you achieved in the project.}

\section{Literature Review}
	\textcolor{gray}{
		\begin{itemize}
			\item What are the possible types of traffic simulation? What are the benefits of each? 
			\item what type of traffic simulation is in \cite{namekawa2005general}? Why is/isn't it suitable for our model?
			\item what type of traffic simulation is used in \cite{sewall2010continuum}? why is/isn't it suitable for out model?
			\item what have we taken from each model and why did we decide to include these attributes?
		\end{itemize}
	}

\section{Requirements and Design}\label{RequirementsAndDesign}
	\textcolor{gray}{What did we set out to achieve?}
	\textcolor{blue}{
	\begin{itemize}
		\item Describe the requirements you set for your project at the beginning and the design you have taken for your project.
		\item  Focus on why you decided to tackle the problem in the way you did, and what effect that had on the design. 
		\item You may also wish to mention the impact of team-working on your requirements and design.
	\end{itemize}
	}

\section{Implementation}
	\textcolor{blue}{Describe the most signicant implementation details, focussing on those where unusual or detailed solutions were required. 
	Quote code fragments where necessary, but remember that the full source code will be included as an appendix. 
	Explain how you tested your software (e.g. unit testing) and the extent to which you tested it. 
	If relevant to your project, explain performance issues and how you tackle}

	\subsection{Documentation}
		\textcolor{gray}{export of JavaDoc, plus help for the user how to use the simulation (i.e. to start, click the start button, to finish, click stop button, etc).}
		
		
	\subsection{Testing}
		\textcolor{blue}{unit testing evidence screenshots, description of typical bugs.}

\section{Team Work}
	\subsection{Roles and Subgroups}
	\subsection{Github}
\section{Evaluation}
	\textcolor{blue}{Critically evaluate your project: what worked well, and what didn't? 
	how did you do relative to your plan? 
	what changes were the result of improved thinking and what changes were forced upon you? 
	how did your team work together? etc. 
	Note that you need to show that you understand the weaknesses in your work as well as its strengths. You may wish to identify relevant future work that could be done on your project}
	
	
\section{Peer Assessment}

	
\bibliographystyle{plain}
\bibliography{../../references}


\end{document}
